\section{Related Work}
\subsection{Video Benchmarks for MLLMs}
Following the success of MLLMs in static image tasks~\citep{SEED-Bench,MMBench,MM-Vet,MMMU}, numerous benchmarks have emerged to evaluate their video understanding capabilities~\citep{MMBench-Video,Video-MME,MVBench,VITATECS,MSQA,TempCompass,OpenEQA,EgoSchema,Video-Bench,TOMATO,SpatialEval,MM-Ego}. 
However, most of them treat videos merely as temporal sequences of 2D images, leaving reasoning within 3D dynamic scenes largely underexplored. 
To address this, recent studies have evaluated the spatial intelligence of MLLMs~\citep{OmniSpatial,MMSI-Video-Bench,SpaceR,VSI-Bench,Cambrian-S,SPAR-Bench}, though they primarily focus on static properties like object size and relative positioning. 
Subsequent spatio-temporal benchmarks~\citep{Dyn-Bench,STI-Bench,OST-Bench,VideoLoom,MLLM-4D,DSI-Bench,DSR-Bench,VLM4D} introduce dynamic evaluations, such as trajectory tracking and speed estimation. 
Despite these advances, existing benchmarks predominantly assess low-level perception rather than high-level reasoning, and their reliance on quantitative predictions often conflates numerical precision with genuine spatio-temporal reasoning capabilities.

\subsection{MLLMs with Spatial Intelligence}
While MLLMs exhibit remarkable visual understanding capabilities~\citep{LLaVA-OneVision-1.5,Claude,LongVILA,LLaVA-OneVision,VILA,GPT-5,Gemini,InternVL3.5,LongVA,LLaVA-Video}, physically grounding them in the 3D world remains challenging. 
This gap has motivated a growing body of work on spatial MLLMs~\citep{SpatialVLM,VLM-3R,3DRS,GeoThinker,SpatialLadder,SpatialCoT,Spatial-SSRL,SpaceR,SoFar,Spatial-MLLM,VST,GeoSR,Think3D,VG-LLM,LLaVA-3D}.
Spatial-MLLM~\citep{Spatial-MLLM} utilizes a spatial encoder initialized with geometric priors to capture 3D structural information. 
Spatial-SSRL~\citep{Spatial-SSRL} proposes a novel self-supervised reinforcement learning paradigm aimed at enhancing LVLM spatial understanding.
Nevertheless, these approaches are largely restricted to static or indoor environments and lack the capacity to explicitly model dynamic scene evolution. 
To overcome this limitation, recent efforts have extended spatial MLLMs toward 4D reasoning for dynamic real-world settings~\citep{LLaVA-4D,Uni4D-LLM}. 
For instance, LLaVA-4D~\citep{LLaVA-4D} integrates 3D spatial coordinates and temporal cues into a unified spatio-temporal prompt, thereby facilitating comprehensive dynamic scene understanding.
